Early-type galaxies with intermediate-scale discs and their ordinary supermassive black holes

### 2015-09-04 papers/ellicular/ellicular.tex
friday

\begin{figure}
\begin{center}
\includegraphics[width=0.49\columnwidth]{images/n1332_image}
\includegraphics[width=0.49\columnwidth]{images/n1332_unsharp} \\
\includegraphics[width=1.03\columnwidth]{images/n1332_decomposition.pdf}
\caption{The galaxy NGC 1332. 
The top panels are the \emph{Spitzer}/IRAC $3.6~\rm \mu m$ image (left) and its unsharp mask (right), 
obtained by dividing the image by a Gaussian-smoothed version of itself. 
The bottom plots display the best-fit model of the surface brightness profile, $\mu$, 
and the ellipticity profile, $\epsilon$, 
along the major-axis, $R_{\rm maj}$. 
The black points are the observed data, which extend out to seven galaxy half-light radii ($\sim 7 \times 20~\rm arcsec$). 
The empty points are data excluded from the fit.   
The color lines represent the individual (PSF-convolved) model components: 
red = S\'ersic (spheroid), blue = exponential (disc). 
The residual profile (data $-$ model) is shown as $\Delta \mu$. 
The horizontal gray dashed line corresponds to an intensity equal to three times the root mean square of the sky background fluctuations. 
$\Delta$ denotes the root mean square scatter of the fit in units of $\rm mag~arcsec^{-2}$.
}
\label{fig:n1332}
\end{center}
\end{figure}

@@

{\bf change: This not only nullifies the need for invoking different evolutionary scenarios for these galaxies 
but it strengthens the significance of the observed (black hole mass)-(spheroid mass) correlation 
and confirms its importance as a fundamental ingredient for theoretical and semi-analytic models 
used to describe the coevolution of spheroids and their central supermassive black holes. }

>>>>

\begin{figure}
\begin{center}
\includegraphics[width=0.49\columnwidth]{images/n1332_image}
\includegraphics[width=0.49\columnwidth]{images/n1332_unsharp} \\
\includegraphics[width=1.03\columnwidth]{images/n1332_decomposition.pdf}
\caption{The galaxy NGC 1332. 
The top panels are the \emph{Spitzer}/IRAC $3.6~\rm \mu m$ image (left) and its unsharp mask (right), 
obtained by dividing the image by a Gaussian-smoothed version of itself. 
The bottom plots display the best-fit model of the surface brightness profile, $\mu$, 
and the ellipticity profile, $\epsilon$, 
along the major-axis, $R_{\rm maj}$. 
The black points are the observed data, which extend out to seven galaxy half-light radii ($\sim 7 \times 20~\rm arcsec$). 
The empty points are data excluded from the fit.   
The color lines represent the individual (PSF-convolved) model components: 
red = S\'ersic (spheroid), blue = S\'ersic (disc). 
The residual profile (data $-$ model) is shown as $\Delta \mu$. 
The horizontal gray dashed line corresponds to an intensity equal to three times the root mean square of the sky background fluctuations. 
$\Delta$ denotes the root mean square scatter of the fit in units of $\rm mag~arcsec^{-2}$.
}
\label{fig:n1332}
\end{center}
\end{figure}

@@

%{\bf change: This not only nullifies the need for invoking different evolutionary scenarios for these galaxies 
%but it strengthens the significance of the observed (black hole mass)-(spheroid mass) correlation 
%and confirms its importance as a fundamental ingredient for theoretical and semi-analytic models 
%used to describe the coevolution of spheroids and their central supermassive black holes. }
